Methods

### 2024-04-05 Sections/Methods.qmd
update
more toc testing
toc

---
title: Methods
date: last-modified
categories: []
code-fold: true
code-tools: true
execute: 
  warning: false
  eval: true
---

@@

>>>>

---
title: Methods
date: last-modified
categories: []
code-fold: true
code-tools: true
# toc: true
# toc-location: body
# toc-title: Contents
execute: 
  warning: false
  eval: true
---

@@

### Procedure
